\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-05-26 paper/ms.tex
ABC writing

ABC works by replacing the proposition $D = D_{\rm observed}$ with a logically
weaker one.

>>>>

A simple ``rejection sampling'' version of
ABC works by sampling the joint prior distribution for the parameters and
data
\begin{align}
p(\theta, D | I) &= p(\theta | I)p(D | \theta, I)
\end{align}
and rejecting samples for which $D \neq D_{\rm observed}$, so that the
samples represent
\begin{align}
p(\theta, D | D = D_{\rm observed}, I) &\propto p(\theta | I)p(D | \theta, I)
\mathds{1}\left[D = D_{\rm observed}\right].
\end{align}
The marginal distribution for $\theta$ is also the conditional distribution
$p(\theta | D = D_{\rm observed}, I)$, that is, the posterior.

This approach is rarely usable in practice because the probability of
generating a dataset that matches the observed one is extremely low.
To work around this, the proposition
So the proposition $D = D_{\rm observed}$ with a logically
weaker one.
